Modelos

### 2019-02-11 20190117_modelos.Rmd
Update 20190117_modelos.Rmd
11feb

```{r library, message=FALSE, warning=FALSE}
options(scipen=999)
library(haven)
library(dplyr)
library(car)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)
library(RItools) #xBalance
library(texreg)
library(lavaan)
library(sjPlot)
library(psych)
library(semPlot)
library(corrplot)
```

>>>>

```{r library, message=FALSE, warning=FALSE}
options(scipen=999)
library(haven)
library(dplyr)
library(car)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)
library(RItools) #xBalance
library(texreg)
library(lavaan)
library(sjPlot)
library(psych)
library(semPlot)
library(corrplot)
